---
title: Differential expression analysis
output:
    html_document:
        code_folding: hide
        toc: true
        toc_float: true
        toc_depth: 3
---

```{r global_options, include=FALSE}
# Sets up global options for rendering RMarkdown into HTML.
knitr::opts_chunk$set(
    warning=FALSE,
    message=FALSE,
    cache.extra_file_dep_1 = file.info('../config/sampletable.tsv')$mtime,
    cache.extra_file_dep_2 = file.info('../data/rnaseq_aggregation/featurecounts.txt')$mtime,
    cache.extra_file_dep_3 = file.info('../data/rnaseq_samples/*/*.kallisto/abundance.h5')$mtime,
    cache.extra_file_dep_4 = file.info('../data/rnaseq_samples/*/*.salmon/quant.sf')$mtime
)
```

```{r lcdbwf, results='hide'}
# Load the lcdbwf R package, which is stored locally.
# This package has many custom functions used throughout this document.
devtools::document('../../../lib/lcdbwf')
devtools::load_all('../../../lib/lcdbwf')
```

```{r libraries}
library(AnnotationHub)
library(BiocParallel)
library(clusterProfiler)
library(cowplot)
library(DESeq2)
library(dplyr)
library(DT)
library(genefilter)
library(ggplot2)
library(gridExtra)
library(plotly)
library(purrr)
library(readr)
library(reshape)
library(tibble)
library(tximport)
library(UpSetR)
```

```{r config}

# HOW TO CONFIGURE ------------------------------------------------------
# Any chunks below that depend on config options should be cached and use one
# or more sections of the config object as arbitrary additional chunk options.
# By convention, we use the argument name "config" although there is nothing
# special about this name e.g.,
#
#      {r, cache=TRUE, config=config$annotation}
#
# Thereafter, any changes to config options under the "annotation" section will then
# invalidate that chunk's cache -- along with any other chunks that also have
# config$annotation included as a chunk option.
#
config <- lcdbwf:::load_config('config.yaml')

# To keep this Rmd streamlined, much of the text is stored in a different file,
# text.yaml, and accessed via the `text` list after it is loaded here.
text <- yaml::yaml.load_file('text.yaml')

parallel <- config$parallel$parallel
if (config$parallel$parallel){
    register(MulticoreParam(config$parallel$cores))
}
```


# Changelog

**Initial results**

Last run: `r date()`

```{r coldata_setup}
# Set up all of the metadata for the samples and experimental design. Use this
# chunk to modify if needed.
colData <- read.table(config$main$sampletable, sep='\t', header=TRUE, stringsAsFactors=FALSE)

# lcdb-wf requires that the first column of the sampletable contains sample
# names. Use that to set the rownames.
rownames(colData) <- colData[,1]
```

```{r dds_initial, cache=TRUE, config=c(config$main, config$toggle$salmon, config$toggle$kallisto)}
# Convert featureCounts gene-level counts into DESeq2 object, and run
# variance-stabiliizing transform.
dds_initial <- lcdbwf:::make_dds(
  list(sampletable=colData, design=~1),
  config=config,
  parallel=config$parallel$parallel
)
vsd <- varianceStabilizingTransformation(dds_initial, blind=TRUE)
```

# Experiment overview

Here is the sample table with metadata used for this analysis:

```{r print_coldata}
exclude.for.printing <- c('featurecounts.path', 'salmon.path', 'kallisto.path',
                          'orig_filename', 'orig_filename_R2', 'layout',
                          'sizeFactor')
colData(dds_initial) %>%
    as.data.frame() %>%
    dplyr::select(-contains(exclude.for.printing)) %>%
    datatable()
```


# Sample similarity and QC

## Clustered heatmap

```{r sample_heatmap, results='asis', cache=TRUE, config=c(text$qc$clustered_heatmap, config$plotting$covariates_for_plots), dependson='dds_initial'}
# Plot a clustered heatmap of sample distances, for QC.
lcdbwf:::mdcat(text$qc$clustered_heatmap)
lcdbwf:::plot_heatmap(vsd, colData, cols_for_grouping=config$plotting$covariates_for_plots)
```

## PCA {.tabset}

### WT {.tabset}

```{r pca_2, results='asis', cache=TRUE, config=c(text$qc$pca, config$plotting$covariates_for_plots), dependson='dds_initial'}
# Plot PCA plots, optionally tabbed with different factors colored, for QC.
lcdbwf:::mdcat(text$qc$pca)

for(group in config$plotting$covariates_for_plots){
    lcdbwf:::mdcat('#### ', paste(group, sep=", "))
    p <- lcdbwf:::plotPCA.ly(vsd, intgroup=group)
    print(htmltools::tagList(ggplotly(p)))
}
```

### NO WT {.tabset}

```{r pca, results='asis', cache=TRUE, config=c(text$qc$pca, config$plotting$covariates_for_plots), dependson='dds_initial'}
# Plot PCA plots, optionally tabbed with different factors colored, for QC.
vsd_no_wt <- vsd[,vsd$group != 'WT']
#lcdbwf:::mdcat('#### NO WT')
for(group in config$plotting$covariates_for_plots){
    lcdbwf:::mdcat('#### ', paste(group, sep=", "))
    p <- lcdbwf:::plotPCA.ly(vsd_no_wt, intgroup=group)
    print(htmltools::tagList(ggplotly(p)))
}
```

```{r sizefactors, results='asis', eval=!(config$toggle$salmon | config$toggle$kallisto)}
# Note that when loading Salmon or Kallisto, DESeq2 does not calculate size
# factors.

lcdbwf:::mdcat(text$sizefactors)
lcdbwf:::mdcat("### Size factors")
p <- lcdbwf:::sizefactors_barplot(dds_initial)
ggplotly(p)

lcdbwf:::mdcat("### Size factors vs total read count")
p <- lcdbwf:::sizefactors_vs_total(dds_initial)
ggplotly(p)
```

```{r dds_list, cache=TRUE, config=config$main}
# Create a list of dds objects used as the basis for differential expression.
#
# May need substantial editing.
lst <- list(
            # NOTE: Delete these for real data!
            # They are just examples to demonstrate functionality.
            #
            # Example 1: simplest case
            main=list(
                sampletable=colData,
                design=~full_guide_grp)

            # Example 2: demonstrates how to filter samples.
            # Note that subset.counts=TRUE is required when filtering.
            #no_rep4=list(
            #    sampletable=colData %>% filter(samplename != 'sample4'),
            #    design=~group,
            #    subset_counts=TRUE
            #),

            # Example 3: use salmon
            #salmon=list(
            #    sampletable=colData,
            #    design=~full_guide_grp,
             #   salmon=TRUE)

           # # Example 4: use kallisto
            #kallisto=list(
            #    sampletable=colData,
            #    design=~full_guide_grp,
            #    kallisto=TRUE)
            # ------------------------------------------------------------------
          )
dds_list <- map(lst, lcdbwf:::make_dds, config=config, parallel=config$parallel$parallel)
```


```{r dds_diagnostics, results='asis', cache=TRUE, dependson='dds_list', config=config$toggle$dds_diagnostics}
if (config$toggle$dds_diagnostics){ lcdbwf:::dds_diagnostics(dds_list, text) }
```

# Differential expression {.tabset}

Now we perform differential expression analysis for the contrasts listed in the
table below.

Under the table are tabs, one for each contrast. Under each contrast's tab,
there are more tabs for the various output.

```{r results_00, dependson='dds_list', cache=TRUE, eval=FALSE}
# Perform differential expression testing.
#
# ------------------------------------------------------------------------------
# To take advantage of caching:
#   - create each list in a different chunk
#   - ensure chunk name starts with "results_"
#   - ensure list name starts with "contr_[index]_". The rest of the name will be used
#     as a readable label for each constrast. [index] is an alphanumeric string 
#     (ex: contr_01_* or contr_2b_*) that will be used to sort contrasts for output files.
#     The index string must contain at least 1 character and cannot contain "_"
#
# This will need substantial editing.
#
# See ?make_results for details.
# ------------------------------------------------------------------------------

# Delete these for real data!
#
# Example 1:
#  - demonstrates creating and manipulating coefficients
#control <- lcdbwf:::dds_coefs('main', group=='control')
#treatment <- lcdbwf:::dds_coefs('main', group=='treatment')
#contr_01_main <- lcdbwf:::make_results(
#  dds_name='main',
 # label='LFC>0',
 # contrast=treatment - control,
 # type='ashr'
#)
```

```{r results_01, dependson='dds_list', cache=TRUE}
contr_01afa_lfc0_WTWT_fc <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c("full_guide_grp", "WT_S", "WT_N"),
  #lfcThreshold=1,
  type="ashr",
  label="Soma-- Neurite WT lfc >0 FeatureC"
)
```

```{r results_011, dependson='dds_list', cache=TRUE}
contr_01afa_lfc1_WTWT_fc <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c("full_guide_grp", "WT_S", "WT_N"),
  lfcThreshold=1,
  type="ashr",
  label="Soma-- Neurite WT lfc >1 FeatureC"
)
```

```{r results_02, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_01af_lfc0_WTWT_sal <- lcdbwf:::make_results(
  dds_name="salmon",
  contrast=c("full_guide_grp", "WT_S", "WT_N"),
  type="ashr",
  label="Soma -- Neurite WT lfc >0 Salmon"
)
```

```{r results_03, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_02af_sg100_SN_TDP <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg100_S_TDP43kd', 'sg100_N_TDP43kd'),
  type='ashr',
  label='NT Soma -- Neurite TDP43kd lfc > 0 FeatureC'
)
```

```{r results_031, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_02af_sg100_SN_TDP_lfc1 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg100_S_TDP43kd', 'sg100_N_TDP43kd'),
  type='ashr',
  lfcTheshold=1,
  label='NT Soma -- Neurite TDP43kd lfc > 1 FeatureC'
)
```

```{r results_04, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_02bf_200NTSS_TDP_lfc0 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg200_S_TDP43kd', 'sg100_S_TDP43kd'),
  type='ashr',
  label='sg200 Soma -- NT Soma TDP43kd lfc > 0 FeatureC'
)
```

```{r results_041, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_02bf_200NTSS_TDP_lfc1 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg200_S_TDP43kd', 'sg100_S_TDP43kd'),
  type='ashr',
  lfcThreshold=1,
  label='sg200 Soma -- NT Soma TDP43kd lfc > 1 FeatureC'
)
```

```{r results_05, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_02cf_200NT_NN_TDP_lfc0 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg200_N_TDP43kd', 'sg100_N_TDP43kd'),
  type='ashr',
  label='sg200 Neurite -- NT Neurite TDP43kd lfc > 0 FeatureC'
)
```

```{r results_051, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_02cf_200NT_NN_TDP_lfc1 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg200_N_TDP43kd', 'sg100_N_TDP43kd'),
  type='ashr',
  lfcThreshold=1,
  label='sg200 Neurite -- NT Neurite TDP43kd lfc > 1 FeatureC'
)
```

```{r results_06, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_03af_NTNT_SN_FUS_lfc0 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg100_S_FUSkd', 'sg100_N_FUSkd'),
  type='ashr',
  label='sg100 Soma -- Neurite FUSkd lfc > 0 FeatureC'
)
```

```{r results_061, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_03af_NTNT_SN_FUS_lfc1 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg100_S_FUSkd', 'sg100_N_FUSkd'),
  type='ashr',
  lfcThreshold=1,
  label='sg100 Soma -- Neurite FUSkd lfc > 1 FeatureC'
)
```

```{r results_07, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_03bf_1152NT_SS_FUS_lfc0 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg1152_S_FUSkd', 'sg100_S_FUSkd'),
  type='ashr',
  label='sg1152 Soma -- NT Soma FUSkd lfc > 0 FeatureC'
)
```

```{r results_071, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_03bf_1152_SS_FUS_lfc1 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg1152_S_FUSkd', 'sg100_S_FUSkd'),
  type='ashr',
  lfcThreshold=1,
  label='sg1152 Soma -- NT Soma FUSkd lfc > 1 FeatureC'
)
```

```{r results_08, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_03cf_1152NT_NN_FUS_lfc0 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg1152_N_FUSkd', 'sg100_N_FUSkd'),
  type='ashr',
  label='sg1152 Neurite -- NT Neurite FUSkd lfc > 0 FeatureC'
)
```

```{r results_081, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_03cf_1152NT_NN_FUS_lfc1 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg1152_N_FUSkd', 'sg100_N_FUSkd'),
  type='ashr',
  lfcThreshold=1,
  label='sg1152 Neurite -- NT Neurite FUSkd lfc > 1 FeatureC'
)
```

```{r results_09, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_04af_1126_SN_HNRN_lfc0 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg1126_S_HNRNPA1kd', 'sg1126_N_HNRNPA1kd'),
  type='ashr',
  label='sg1126 Soma -- Neurite HNRNPA1kd lfc > 0 FeatureC'
)
```

```{r results_09_1, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_04af_1126_SN_HNRN_lfc1 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg1126_S_HNRNPA1kd', 'sg1126_N_HNRNPA1kd'),
  type='ashr',
  lfcThreshold=1,
  label='sg1126 Soma -- Neurite HNRNPA1kd lfc > 1 FeatureC'
)
```

```{r results_10, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_04bf_1128_1126_SS_HNRN_lfc0 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg1128_S_HNRNPA1kd', 'sg1126_S_HNRNPA1kd'),
  type='ashr',
  label='sg1128 Soma -- sg1126 Soma HNRNPA1kd lfc > 0 FeatureC'
)
```

```{r results_10_1, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_04bf_1128_1126_SS_HNRN_lfc1 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg1128_S_HNRNPA1kd', 'sg1126_S_HNRNPA1kd'),
  type='ashr',
  lfcThreshold=1,
  label='sg1128 Soma -- sg1126 Soma HNRNPA1kd lfc > 1 FeatureC'
)
```

```{r results_11, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_04cf_1128_1126_NN_HNRN_lfc0 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg1128_N_HNRNPA1kd', 'sg1126_N_HNRNPA1kd'),
  type='ashr',
  label='sg1128 Neurite -- sg1126 Neurite HNRNPA1kd lfc > 0 FeatureC'
)
```

```{r results_11_1, dependson='dds_list', cache=TRUE}
# main contrasts first, then salmon and kallisto
contr_04cf_1128_1126_NN_HNRN_lfc1 <- lcdbwf:::make_results(
  dds_name="main",
  contrast=c('full_guide_grp', 'sg1128_N_HNRNPA1kd', 'sg1126_N_HNRNPA1kd'),
  type='ashr',
  lfcThreshold=1,
  label='sg1128 Neurite -- sg1126 Neurite HNRNPA1kd lfc > 1 FeatureC'
)
```

```{r results_12, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_02as_jlfc0 <- lcdbwf:::make_results(
  dds_name="salmon",
  contrast=c('full_guide_grp', 'sg100_S_TDP43kd', 'sg100_N_TDP43kd'),
  type='ashr',
  label='sg100 Soma -- Neurite TDP43kd lfc > 0 Salmon'
)
```

```{r results_13, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_02bs_klfc0 <- lcdbwf:::make_results(
  dds_name="salmon",
  contrast=c('full_guide_grp', 'sg200_S_TDP43kd', 'sg100_S_TDP43kd'),
  type='ashr',
  label='sg200 Soma -- sg100 Soma TDP43kd lfc > 0 Salmon'
)
```

```{r results_14, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_02cs_lfc0 <- lcdbwf:::make_results(
  dds_name="salmon",
  contrast=c('full_guide_grp', 'sg200_N_TDP43kd', 'sg100_N_TDP43kd'),
  type='ashr',
  label='sg200 Neurite -- sg100 Neurite TDP43kd lfc > 0 Salmon'
)
```

```{r results_15, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_03as_lfc0 <- lcdbwf:::make_results(
  dds_name="salmon",
  contrast=c('full_guide_grp', 'sg100_S_FUSkd', 'sg100_N_FUSkd'),
  type='ashr',
  label='sg100 Soma -- Neurite FUSkd lfc > 0 Salmon'
)
```

```{r results_16, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_03bs_lfc0 <- lcdbwf:::make_results(
  dds_name="salmon",
  contrast=c('full_guide_grp', 'sg1152_S_FUSkd', 'sg100_S_FUSkd'),
  type='ashr',
  label='sg1152 Soma -- sg100 Soma FUSkd lfc > 0 Salmon'
)
```

```{r results_17, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_03cs_lfc0 <- lcdbwf:::make_results(
  dds_name="salmon",
  contrast=c('full_guide_grp', 'sg1152_N_FUSkd', 'sg100_N_FUSkd'),
  type='ashr',
  label='sg1152 Neurite -- sg100 Neurite FUSkd lfc > 0 Salmon'
)
```

```{r results_18, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_04as_lfc0 <- lcdbwf:::make_results(
  dds_name="salmon",
  contrast=c('full_guide_grp', 'sg1126_S_HNRNPA1kd', 'sg1126_N_HNRNPA1kd'),
  type='ashr',
  label='sg1126 Soma -- Neurite HNRNPA1kd lfc > 0 Salmon'
)
```

```{r results_19, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_04bs_lfc0 <- lcdbwf:::make_results(
  dds_name="salmon",
  contrast=c('full_guide_grp', 'sg1128_S_HNRNPA1kd', 'sg1126_S_HNRNPA1kd'),
  type='ashr',
  label='sg1128 Soma -- sg1126 Soma HNRNPA1kd lfc > 0 Salmon'
)
```

```{r results_20, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_04cs_lfc0 <- lcdbwf:::make_results(
  dds_name="salmon",
  contrast=c('full_guide_grp', 'sg1128_N_HNRNPA1kd', 'sg1126_N_HNRNPA1kd'),
  type='ashr',
  label='sg1128 Neurite -- sg1126 Neurite HNRNPA1kd lfc > 0 Salmon'
)
```

```{r results_21, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_02ak_lfc0 <- lcdbwf:::make_results(
  dds_name="kallisto",
  contrast=c('full_guide_grp', 'sg100_S_TDP43kd', 'sg100_N_TDP43kd'),
  type='ashr',
  label='sg100 Soma -- Neurite TDP43kd lfc > 0 kallisto'
)
```

```{r results_22, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_02bk_lfc0 <- lcdbwf:::make_results(
  dds_name="kallisto",
  contrast=c('full_guide_grp', 'sg200_S_TDP43kd', 'sg100_S_TDP43kd'),
  type='ashr',
  label='sg200 Soma -- sg100 Soma TDP43kd lfc > 0 kallisto'
)
```

```{r results_23, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_02ck_lfc0 <- lcdbwf:::make_results(
  dds_name="kallisto",
  contrast=c('full_guide_grp', 'sg200_N_TDP43kd', 'sg100_N_TDP43kd'),
  type='ashr',
  label='sg200 Neurite -- sg100 Neurite TDP43kd lfc > 0 kallisto'
)
```

```{r results_24, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_03ak_lfc0 <- lcdbwf:::make_results(
  dds_name="kallisto",
  contrast=c('full_guide_grp', 'sg100_S_FUSkd', 'sg100_N_FUSkd'),
  type='ashr',
  label='sg100 Soma -- Neurite FUSkd lfc > 0 kallisto'
)
```

```{r results_25, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_03bk_lfc0 <- lcdbwf:::make_results(
  dds_name="kallisto",
  contrast=c('full_guide_grp', 'sg1152_S_FUSkd', 'sg100_S_FUSkd'),
  type='ashr',
  label='sg1152 Soma -- sg100 Soma FUSkd lfc > 0 kallisto'
)
```

```{r results_26, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_03ck_lfc0 <- lcdbwf:::make_results(
  dds_name="kallisto",
  contrast=c('full_guide_grp', 'sg1152_N_FUSkd', 'sg100_N_FUSkd'),
  type='ashr',
  label='sg1152 Neurite -- sg100 Neurite FUSkd lfc > 0 kallisto'
)
```

```{r results_27, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_04ak_lfc0 <- lcdbwf:::make_results(
  dds_name="kallisto",
  contrast=c('full_guide_grp', 'sg1126_S_HNRNPA1kd', 'sg1126_N_HNRNPA1kd'),
  type='ashr',
  label='sg1126 Soma -- Neurite HNRNPA1kd lfc > 0 kallisto'
)
```

```{r results_28, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_04bk_lfc0 <- lcdbwf:::make_results(
  dds_name="kallisto",
  contrast=c('full_guide_grp', 'sg1128_S_HNRNPA1kd', 'sg1126_S_HNRNPA1kd'),
  type='ashr',
  label='sg1128 Soma -- sg1126 Soma HNRNPA1kd lfc > 0 kallisto'
)
```

```{r results_29, dependson='dds_list', cache=TRUE, eval=FALSE}
contr_04ck_lfc0 <- lcdbwf:::make_results(
  dds_name="kallisto",
  contrast=c('full_guide_grp', 'sg1128_N_HNRNPA1kd', 'sg1126_N_HNRNPA1kd'),
  type='ashr',
  label='sg1128 Neurite -- sg1126 Neurite HNRNPA1kd lfc > 0 kallisto'
)
```

```{r assemble_variables, cache=TRUE, config=config$annotation, dependson=knitr::all_labels()[grepl("^results_", knitr::all_labels())]}
res_list <- lcdbwf:::collect_objects("^contr_[^_]+_")
res_list <- lcdbwf:::attach_extra(res_list, config)
```

```{r summary, results='asis'}
lcdbwf:::folded_markdown(text$results_table, "Help for table")
lcdbwf:::summarize_res_list(res_list) %>% datatable
```

```{r reportresults, results='asis', config=c(text$results_plots, config$toggle$results_diagnostics, config$plotting$diagnostics_results_names), dependson='assemble_variables', cache=TRUE}
# Create nested tabs showing the results.
# First level of tabs will be labels of results; second level will be different
# output (MA plot, volcano plot, etc)
lcdbwf:::build_results_tabs(res_list, dds_list, config, text)
```

```{r upsetplots, results='asis', eval=length(res_list)>1, config=config$annotation}
# Compare overlap across multiple differential expression contrasts.
lcdbwf:::mdcat(text$upset_plots)
lcdbwf:::plot_upsets(res_list, label_column=config$annotation$label_column)
```

# Exported results

```{r excel, results='asis'}
lcdbwf:::exported_excel(res_list, dds_list, file='results/consolidated_results.xlsx')
```

Here is a single Excel file with one worksheet for each contrast: [results/consolidated_results.xlsx](results/consolidated_results.xlsx)

Alternatively, the files below are TSVs that can be opened in Excel or used
progammatically with downstream tools:

```{r write_output, results='asis'}
# Write out files for full and each selection, and create a link to them in the
# HTML generated by this RMarkdown.
tbl <- lcdbwf:::exported_tsvs(res_list)
knitr::kable(tbl, row.names=FALSE)
```

```{r combined_rds, cache=TRUE, dependson='assemble_variables'}
obj <- lcdbwf:::compose_results(res_list, dds_list)
saveRDS(obj, file='combined.Rds', compress=FALSE)
```


# Session info
For reproducibility purposes, here is the output of `sessionInfo()` showing the
versions of all packages used here.

```{r sessioninfo}
sessionInfo()
```
